A new breeding crossover approach for evolutionary algorithms

### 2023-09-22 paper.tex
Final Update (Turnitin ready)
Condensed Tables Update

@@

    \begin{table}[]
    \scriptsize
    \centering
    \caption{Condensed ALCA evaluation results for the CEC-2017 functions running on ten dimensions for alternatives One Point and Continuous Range crossover.}\label{tab.condensed_evaluation_10D}
    \begin{tabular}{@{}lllllllll@{}}
    \toprule
    \multicolumn{9}{c}{\textbf{ALCA . CEC-2017 . 10D}} \\ \midrule
    Crossover &  & \multicolumn{3}{c}{One Point Xover} &  & \multicolumn{3}{c}{Cont. Range Xover} \\
    Fx &  & Mean & Std. Dev. & Z &  & Mean & Std. Dev. & Z \\
    F1 &  & 2.14E+03 & 2.14E+03 & 5.42E+00 &  & 4.43E+02 & 6.46E+02 & \textbf{-5.42E+00} \\
    F2 &  & 1.81E-03 & 2.63E-03 & 2.38E+00 &  & 8.54E-04 & 1.16E-03 & \textbf{-2.38E+00} \\
    F3 &  & 4.19E-04 & 1.16E-03 & 2.49E+00 &  & 1.33E-05 & 2.20E-05 & \textbf{-2.49E+00} \\
    F4 &  & 6.00E+00 & 1.31E+01 & 2.00E+00 &  & 2.31E+00 & 1.78E+00 & \textbf{-2.00E+00} \\
    F5 &  & 1.53E+01 & 7.06E+00 & 2.45E+00 &  & 1.24E+01 & 4.14E+00 & \textbf{-2.45E+00} \\
    F6 &  & 6.05E-04 & 9.22E-04 & -1.43E+00 &  & 2.53E-03 & 9.61E-03 & 1.43E+00 \\
    F7 &  & 3.15E+01 & 9.06E+00 & 2.26E+00 &  & 2.76E+01 & 8.38E+00 & \textbf{-2.26E+00} \\
    F8 &  & 1.78E+01 & 7.38E+00 & 8.00E+00 &  & 8.62E+00 & 3.53E+00 & \textbf{-8.00E+00} \\
    F9 &  & 2.02E+01 & 2.24E+01 & 1.85E+00 &  & 1.25E+01 & 1.96E+01 & \textbf{-1.85E+00} \\
    F10 &  & 4.96E+02 & 2.26E+02 & \textbf{-2.02E+00} &  & 5.94E+02 & 2.63E+02 & 2.02E+00 \\
    F11 &  & 1.16E+01 & 6.01E+00 & \textbf{-2.44E+00} &  & 1.49E+01 & 7.48E+00 & 2.44E+00 \\
    F12 &  & 1.70E+04 & 1.99E+04 & 2.00E+00 &  & 1.10E+04 & 8.21E+03 & \textbf{-2.00E+00} \\
    F13 &  & 7.39E+03 & 8.16E+03 & 1.08E+00 &  & 5.94E+03 & 5.03E+03 & -1.08E+00 \\
    F14 &  & 3.24E+02 & 6.05E+02 & 4.65E-01 &  & 2.67E+02 & 6.34E+02 & -4.65E-01 \\
    F15 &  & 5.70E+02 & 1.31E+03 & 1.25E+00 &  & 3.07E+02 & 7.46E+02 & -1.25E+00 \\
    F16 &  & 1.56E+02 & 1.28E+02 & 5.05E-01 &  & 1.43E+02 & 1.18E+02 & -5.05E-01 \\
    F17 &  & 3.17E+01 & 3.65E+01 & 1.81E+00 &  & 2.11E+01 & 1.98E+01 & \textbf{-1.81E+00} \\
    F18 &  & 2.26E+03 & 2.88E+03 & 9.03E-01 &  & 1.73E+03 & 3.06E+03 & -9.03E-01 \\
    F19 &  & 1.88E+03 & 3.24E+03 & 4.11E-01 &  & 1.63E+03 & 2.95E+03 & -4.11E-01 \\
    F20 &  & 9.50E+00 & 8.32E+00 & -1.35E+00 &  & 1.20E+01 & 9.92E+00 & 1.35E+00 \\
    F21 &  & 1.15E+02 & 3.86E+01 & 4.93E-02 &  & 1.15E+02 & 3.58E+01 & -4.93E-02 \\
    F22 &  & 1.00E+02 & 2.07E+01 & \textbf{-2.57E+00} &  & 1.08E+02 & 8.70E+00 & 2.57E+00 \\
    F23 &  & 3.21E+02 & 7.31E+00 & \textbf{-2.53E+00} &  & 3.25E+02 & 8.91E+00 & 2.53E+00 \\
    F24 &  & 3.28E+02 & 8.06E+01 & 5.36E+00 &  & 2.15E+02 & 1.28E+02 & \textbf{-5.36E+00} \\
    F25 &  & 4.35E+02 & 2.61E+01 & 1.39E+00 &  & 4.28E+02 & 2.41E+01 & -1.39E+00 \\
    F26 &  & 3.99E+02 & 1.25E+02 & 7.55E-01 &  & 3.82E+02 & 9.35E+01 & -7.55E-01 \\
    F27 &  & 3.88E+02 & 1.03E+01 & -5.43E-01 &  & 3.90E+02 & 1.13E+01 & 5.43E-01 \\
    F28 &  & 4.11E+02 & 7.92E+01 & 1.93E+00 &  & 3.80E+02 & 8.46E+01 & \textbf{-1.93E+00} \\
    F29 &  & 3.00E+02 & 4.32E+01 & 7.44E-01 &  & 2.94E+02 & 3.30E+01 & -7.44E-01 \\
    F30 &  & 3.21E+02 & 1.52E+02 & -7.14E-01 &  & 3.44E+02 & 1.81E+02 & 7.14E-01 \\
    \textbf{Total (W)} &  & \multicolumn{2}{c}{\textbf{One Point Xover}} & \multicolumn{1}{c}{\textbf{4 of 30}} &  & \multicolumn{2}{c}{\textbf{Cont. Range Xover}} & \multicolumn{1}{c}{\textbf{12 of 30}} \\ \bottomrule
    \end{tabular}
    \end{table}

    \begin{table}[]
    \scriptsize
    \centering
    \caption{Condensed ALCA evaluation results for the CEC-2017 functions running on thirty dimensions for alternatives One Point and Continuous Range crossover.}\label{tab.condensed_evaluation_30D}    
    \begin{tabular}{@{}lllllllll@{}}
    \toprule
    \multicolumn{9}{c}{\textbf{ALCA . CEC-2017 . 30D}} \\ \midrule
    Crossover &  & \multicolumn{3}{c}{One Point Xover} &  & \multicolumn{3}{c}{Cont. Range Xover} \\
    Fx &  & Mean & Std. Dev. & Z &  & Mean & Std. Dev. & Z \\
    F1 &  & 4.92E+03 & 6.21E+03 & 1.60E+00 &  & 3.35E+03 & 3.33E+03 & -1.60E+00 \\
    F2 &  & 9.21E+06 & 4.77E+07 & 1.37E+00 &  & 6.96E+04 & 2.50E+05 & -1.37E+00 \\
    F3 &  & 1.17E+02 & 1.18E+02 & 4.33E+00 &  & 4.16E+01 & 3.85E+01 & \textbf{-4.33E+00} \\
    F4 &  & 7.17E+01 & 3.14E+01 & -5.29E-01 &  & 7.46E+01 & 2.52E+01 & 5.29E-01 \\
    F5 &  & 9.38E+01 & 2.41E+01 & 4.61E-01 &  & 9.18E+01 & 2.04E+01 & -4.61E-01 \\
    F6 &  & 4.67E-03 & 1.02E-02 & \textbf{-2.42E+00} &  & 2.28E-02 & 5.26E-02 & 2.42E+00 \\
    F7 &  & 1.55E+02 & 3.04E+01 & -3.88E-01 &  & 1.58E+02 & 3.44E+01 & 3.88E-01 \\
    F8 &  & 9.94E+01 & 2.43E+01 & 6.82E+00 &  & 7.29E+01 & 1.32E+01 & \textbf{-6.82E+00} \\
    F9 &  & 1.37E+03 & 7.21E+02 & 4.60E+00 &  & 8.19E+02 & 4.64E+02 & \textbf{-4.60E+00} \\
    F10 &  & 2.79E+03 & 5.59E+02 & \textbf{-2.22E+00} &  & 3.02E+03 & 4.63E+02 & 2.22E+00 \\
    F11 &  & 7.31E+01 & 2.72E+01 & -1.09E+00 &  & 7.90E+01 & 2.75E+01 & 1.09E+00 \\
    F12 &  & 2.18E+05 & 1.94E+05 & 4.61E+00 &  & 8.73E+04 & 5.95E+04 & \textbf{-4.61E+00} \\
    F13 &  & 1.95E+04 & 2.73E+04 & 2.09E+00 &  & 1.10E+04 & 8.96E+03 & \textbf{-2.09E+00} \\
    F14 &  & 2.22E+04 & 2.14E+04 & 2.83E+00 &  & 1.27E+04 & 1.06E+04 & \textbf{-2.83E+00} \\
    F15 &  & 1.25E+04 & 1.41E+04 & 4.96E+00 &  & 2.37E+03 & 3.82E+03 & \textbf{-4.96E+00} \\
    F16 &  & 1.26E+03 & 3.45E+02 & 1.49E-01 &  & 1.26E+03 & 2.49E+02 & -1.49E-01 \\
    F17 &  & 6.02E+02 & 1.76E+02 & 1.17E+00 &  & 5.54E+02 & 2.36E+02 & -1.17E+00 \\
    F18 &  & 1.29E+05 & 1.17E+05 & 2.92E+00 &  & 7.44E+04 & 6.27E+04 & \textbf{-2.92E+00} \\
    F19 &  & 9.78E+03 & 1.16E+04 & 3.04E+00 &  & 4.38E+03 & 5.08E+03 & \textbf{-3.04E+00} \\
    F20 &  & 4.83E+02 & 1.69E+02 & 1.02E-01 &  & 4.79E+02 & 2.03E+02 & -1.02E-01 \\
    F21 &  & 3.03E+02 & 2.44E+01 & 4.40E+00 &  & 2.85E+02 & 1.62E+01 & \textbf{-4.40E+00} \\
    F22 &  & 1.76E+03 & 1.72E+03 & 6.07E+00 &  & 2.16E+02 & 5.84E+02 & \textbf{-6.07E+00} \\
    F23 &  & 4.62E+02 & 3.06E+01 & \textbf{-5.27E+00} &  & 5.05E+02 & 4.97E+01 & 5.27E+00 \\
    F24 &  & 6.45E+02 & 7.43E+01 & \textbf{-2.31E+00} &  & 6.78E+02 & 7.03E+01 & 2.31E+00 \\
    F25 &  & 3.85E+02 & 1.49E+01 & \textbf{-3.06E+00} &  & 3.97E+02 & 2.40E+01 & 3.06E+00 \\
    F26 &  & 2.40E+03 & 4.88E+02 & -1.23E+00 &  & 2.61E+03 & 1.17E+03 & 1.23E+00 \\
    F27 &  & 4.94E+02 & 1.23E+01 & 2.98E-01 &  & 4.93E+02 & 1.95E+01 & -2.98E-01 \\
    F28 &  & 4.63E+02 & 4.29E+01 & 9.26E+00 &  & 3.98E+02 & 2.58E+01 & \textbf{-9.26E+00} \\
    F29 &  & 9.22E+02 & 2.36E+02 & 1.55E+00 &  & 8.56E+02 & 2.00E+02 & -1.55E+00 \\
    F30 &  & 3.53E+03 & 4.15E+03 & 4.09E+00 &  & 1.08E+03 & 1.04E+03 & \textbf{-4.09E+00} \\
    \multicolumn{1}{c}{\textbf{Total (W)}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{One Point Xover}} & \multicolumn{1}{c}{\textbf{5 of 30}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{Cont. Range Xover}} & \multicolumn{1}{c}{\textbf{13 of 30}} \\ \bottomrule
    \end{tabular}
    \end{table}

>>>>

    \begin{table}[]
    \scriptsize
    \centering
    \caption{Condensed ALCA evaluation results for the CEC-2017 functions running on ten dimensions for alternatives One Point and Continuous Range crossover.}\label{tab.condensed_evaluation_10D}    
    \begin{tabular}{@{}cllllllll@{}}
    \toprule
    \multicolumn{9}{c}{\textbf{ALCA   . CEC-2017 Benchmark Functions . 10 Dim}} \\ \midrule
    \textbf{Crossover} & \textbf{} & \multicolumn{3}{c}{\textbf{One Point   Xover}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{3}{c}{\textbf{Cont. Range   Xover}} \\
    Fx &  & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Std. Dev.} & \multicolumn{1}{c}{Z} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Std. Dev.} & \multicolumn{1}{c}{Z} \\
    F1 &  & 2.1389E+03 & 2.1399E+03 & 5.4192E+00 &  & 4.4273E+02 & 6.4605E+02 & \textbf{-5.4192E+00} \\
    F2 &  & 1.8100E-03 & 2.6299E-03 & 2.3752E+00 &  & 8.5385E-04 & 1.1614E-03 & \textbf{-2.3752E+00} \\
    F3 &  & 4.1859E-04 & 1.1643E-03 & 2.4856E+00 &  & 1.3284E-05 & 2.1996E-05 & \textbf{-2.4856E+00} \\
    F4 &  & 6.0009E+00 & 1.3061E+01 & 1.9980E+00 &  & 2.3131E+00 & 1.7796E+00 & \textbf{-1.9980E+00} \\
    F5 &  & 1.5256E+01 & 7.0569E+00 & 2.4517E+00 &  & 1.2447E+01 & 4.1425E+00 & \textbf{-2.4517E+00} \\
    F6 &  & 6.0531E-04 & 9.2170E-04 & -1.4267E+00 &  & 2.5341E-03 & 9.6104E-03 & 1.4267E+00 \\
    F7 &  & 3.1484E+01 & 9.0577E+00 & 2.2567E+00 &  & 2.7585E+01 & 8.3786E+00 & \textbf{-2.2567E+00} \\
    F8 &  & 1.7792E+01 & 7.3832E+00 & 8.0015E+00 &  & 8.6230E+00 & 3.5299E+00 & \textbf{-8.0015E+00} \\
    F9 &  & 2.0213E+01 & 2.2424E+01 & 1.8477E+00 &  & 1.2506E+01 & 1.9608E+01 & \textbf{-1.8477E+00} \\
    F10 &  & 4.9585E+02 & 2.2558E+02 & \textbf{-2.0236E+00} &  & 5.9412E+02 & 2.6338E+02 & 2.0236E+00 \\
    F11 &  & 1.1599E+01 & 6.0084E+00 & \textbf{-2.4372E+00} &  & 1.4872E+01 & 7.4763E+00 & 2.4372E+00 \\
    F12 &  & 1.6980E+04 & 1.9876E+04 & 1.9990E+00 &  & 1.0960E+04 & 8.2128E+03 & \textbf{-1.9990E+00} \\
    F13 &  & 7.3909E+03 & 8.1574E+03 & 1.0784E+00 &  & 5.9436E+03 & 5.0303E+03 & -1.0784E+00 \\
    F14 &  & 3.2387E+02 & 6.0517E+02 & 4.6471E-01 &  & 2.6685E+02 & 6.3381E+02 & -4.6471E-01 \\
    F15 &  & 5.7005E+02 & 1.3121E+03 & 1.2452E+00 &  & 3.0689E+02 & 7.4575E+02 & -1.2452E+00 \\
    F16 &  & 1.5553E+02 & 1.2806E+02 & 5.0519E-01 &  & 1.4323E+02 & 1.1771E+02 & -5.0519E-01 \\
    F17 &  & 3.1678E+01 & 3.6537E+01 & 1.8131E+00 &  & 2.1124E+01 & 1.9819E+01 & \textbf{-1.8131E+00} \\
    F18 &  & 2.2591E+03 & 2.8803E+03 & 9.0297E-01 &  & 1.7279E+03 & 3.0584E+03 & -9.0297E-01 \\
    F19 &  & 1.8843E+03 & 3.2365E+03 & 4.1079E-01 &  & 1.6323E+03 & 2.9529E+03 & -4.1079E-01 \\
    F20 &  & 9.5026E+00 & 8.3167E+00 & -1.3542E+00 &  & 1.1957E+01 & 9.9176E+00 & 1.3542E+00 \\
    F21 &  & 1.1492E+02 & 3.8643E+01 & 4.9288E-02 &  & 1.1455E+02 & 3.5773E+01 & -4.9288E-02 \\
    F22 &  & 1.0005E+02 & 2.0717E+01 & \textbf{-2.5672E+00} &  & 1.0813E+02 & 8.6974E+00 & 2.5672E+00 \\
    F23 &  & 3.2068E+02 & 7.3128E+00 & \textbf{-2.5291E+00} &  & 3.2476E+02 & 8.9080E+00 & 2.5291E+00 \\
    F24 &  & 3.2831E+02 & 8.0609E+01 & 5.3612E+00 &  & 2.1484E+02 & 1.2786E+02 & \textbf{-5.3612E+00} \\
    F25 &  & 4.3486E+02 & 2.6137E+01 & 1.3872E+00 &  & 4.2795E+02 & 2.4061E+01 & -1.3872E+00 \\
    F26 &  & 3.9878E+02 & 1.2472E+02 & 7.5476E-01 &  & 3.8231E+02 & 9.3517E+01 & -7.5476E-01 \\
    F27 &  & 3.8835E+02 & 1.0299E+01 & -5.4299E-01 &  & 3.8951E+02 & 1.1293E+01 & 5.4299E-01 \\
    F28 &  & 4.1119E+02 & 7.9226E+01 & 1.9297E+00 &  & 3.7987E+02 & 8.4606E+01 & \textbf{-1.9297E+00} \\
    F29 &  & 2.9963E+02 & 4.3225E+01 & 7.4383E-01 &  & 2.9396E+02 & 3.3009E+01 & -7.4383E-01 \\
    F30 &  & 3.2080E+02 & 1.5217E+02 & -7.1382E-01 &  & 3.4441E+02 & 1.8071E+02 & 7.1382E-01 \\
    \textbf{Total   (W)} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{One Point   Xover}} & \multicolumn{1}{c}{\textbf{4 of 30}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{Cont. Range   Xover}} & \multicolumn{1}{c}{\textbf{12 of 30}} \\ \bottomrule
    \end{tabular}
    \end{table}

    \begin{table}[]
    \scriptsize
    \centering
    \caption{Condensed ALCA evaluation results for the CEC-2017 functions running on thirty dimensions for alternatives One Point and Continuous Range crossover.}\label{tab.condensed_evaluation_30D}
    \begin{tabular}{@{}cllllllll@{}}
    \toprule
    \multicolumn{9}{c}{\textbf{ALCA   . CEC-2017 Benchmark Functions . 30 Dim}} \\ \midrule
    \textbf{Crossover} & \textbf{} & \multicolumn{3}{c}{\textbf{One Point   Xover}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{3}{c}{\textbf{Cont. Range   Xover}} \\
    Fx &  & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Std. Dev.} & \multicolumn{1}{c}{Z} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Std. Dev.} & \multicolumn{1}{c}{Z} \\
    F1 &  & 4.9221E+03 & 6.2052E+03 & 1.5981E+00 &  & 3.3461E+03 & 3.3306E+03 & -1.5981E+00 \\
    F2 &  & 9.2072E+06 & 4.7678E+07 & 1.3686E+00 &  & 6.9569E+04 & 2.4985E+05 & -1.3686E+00 \\
    F3 &  & 1.1683E+02 & 1.1804E+02 & 4.3284E+00 &  & 4.1582E+01 & 3.8455E+01 & \textbf{-4.3284E+00} \\
    F4 &  & 7.1658E+01 & 3.1444E+01 & -5.2921E-01 &  & 7.4645E+01 & 2.5202E+01 & 5.2921E-01 \\
    F5 &  & 9.3827E+01 & 2.4093E+01 & 4.6068E-01 &  & 9.1790E+01 & 2.0430E+01 & -4.6068E-01 \\
    F6 &  & 4.6723E-03 & 1.0247E-02 & \textbf{-2.4217E+00} &  & 2.2849E-02 & 5.2614E-02 & 2.4217E+00 \\
    F7 &  & 1.5523E+02 & 3.0419E+01 & -3.8825E-01 &  & 1.5772E+02 & 3.4361E+01 & 3.8825E-01 \\
    F8 &  & 9.9361E+01 & 2.4339E+01 & 6.8232E+00 &  & 7.2924E+01 & 1.3162E+01 & \textbf{-6.8232E+00} \\
    F9 &  & 1.3710E+03 & 7.2076E+02 & 4.6028E+00 &  & 8.1853E+02 & 4.6408E+02 & \textbf{-4.6028E+00} \\
    F10 &  & 2.7912E+03 & 5.5872E+02 & \textbf{-2.2216E+00} &  & 3.0169E+03 & 4.6303E+02 & 2.2216E+00 \\
    F11 &  & 7.3052E+01 & 2.7205E+01 & -1.0895E+00 &  & 7.8958E+01 & 2.7541E+01 & 1.0895E+00 \\
    F12 &  & 2.1831E+05 & 1.9392E+05 & 4.6137E+00 &  & 8.7259E+04 & 5.9525E+04 & \textbf{-4.6137E+00} \\
    F13 &  & 1.9452E+04 & 2.7290E+04 & 2.0901E+00 &  & 1.1046E+04 & 8.9591E+03 & \textbf{-2.0901E+00} \\
    F14 &  & 2.2151E+04 & 2.1428E+04 & 2.8255E+00 &  & 1.2691E+04 & 1.0610E+04 & \textbf{-2.8255E+00} \\
    F15 &  & 1.2499E+04 & 1.4069E+04 & 4.9618E+00 &  & 2.3697E+03 & 3.8202E+03 & \textbf{-4.9618E+00} \\
    F16 &  & 1.2641E+03 & 3.4529E+02 & 1.4923E-01 &  & 1.2552E+03 & 2.4941E+02 & -1.4923E-01 \\
    F17 &  & 6.0224E+02 & 1.7565E+02 & 1.1651E+00 &  & 5.5424E+02 & 2.3605E+02 & -1.1651E+00 \\
    F18 &  & 1.2865E+05 & 1.1706E+05 & 2.9170E+00 &  & 7.4398E+04 & 6.2747E+04 & \textbf{-2.9170E+00} \\
    F19 &  & 9.7805E+03 & 1.1607E+04 & 3.0408E+00 &  & 4.3849E+03 & 5.0850E+03 & \textbf{-3.0408E+00} \\
    F20 &  & 4.8317E+02 & 1.6940E+02 & 1.0238E-01 &  & 4.7938E+02 & 2.0307E+02 & -1.0238E-01 \\
    F21 &  & 3.0294E+02 & 2.4353E+01 & 4.3999E+00 &  & 2.8493E+02 & 1.6184E+01 & \textbf{-4.3999E+00} \\
    F22 &  & 1.7571E+03 & 1.7169E+03 & 6.0688E+00 &  & 2.1583E+02 & 5.8436E+02 & \textbf{-6.0688E+00} \\
    F23 &  & 4.6160E+02 & 3.0564E+01 & \textbf{-5.2747E+00} &  & 5.0468E+02 & 4.9672E+01 & 5.2747E+00 \\
    F24 &  & 6.4513E+02 & 7.4299E+01 & \textbf{-2.3148E+00} &  & 6.7829E+02 & 7.0328E+01 & 2.3148E+00 \\
    F25 &  & 3.8492E+02 & 1.4918E+01 & \textbf{-3.0635E+00} &  & 3.9704E+02 & 2.3987E+01 & 3.0635E+00 \\
    F26 &  & 2.3955E+03 & 4.8813E+02 & -1.2340E+00 &  & 2.6143E+03 & 1.1683E+03 & 1.2340E+00 \\
    F27 &  & 4.9415E+02 & 1.2280E+01 & 2.9755E-01 &  & 4.9319E+02 & 1.9531E+01 & -2.9755E-01 \\
    F28 &  & 4.6268E+02 & 4.2897E+01 & 9.2609E+00 &  & 3.9779E+02 & 2.5756E+01 & \textbf{-9.2609E+00} \\
    F29 &  & 9.2249E+02 & 2.3560E+02 & 1.5461E+00 &  & 8.5552E+02 & 2.0043E+02 & -1.5461E+00 \\
    F30 &  & 3.5332E+03 & 4.1540E+03 & 4.0881E+00 &  & 1.0823E+03 & 1.0372E+03 & \textbf{-4.0881E+00} \\
    \textbf{Total   (W)} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{One Point   Xover}} & \multicolumn{1}{c}{\textbf{5 of 30}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{Cont. Range   Xover}} & \multicolumn{1}{c}{\textbf{13 of 30}} \\ \bottomrule
    \end{tabular}
    \end{table}

@@
